---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# inventoRy 

<!-- badges: start -->
<!-- badges: end -->

The  inventoRy package offers  nonparametric bootstrap and conventional parametric approaches for estimating inventory policy decisions such as the reorder point (ROP) and safety stocks (SS). These functions are for single item inventories under the continuous review (periodic review functions are in development) inventory policy using either the cycle service level (CSL) or fill rate (FR) targets. 

The nonparametric bootstrap approach is particularly useful when users are unsure if the shape of the LTD  distributions follows a conventional parametric form or nonparametric form. Bootstrap works well when distributions of lead time demand follow non-standard shapes and when conventional normal and gamma estimates can be biased (Fig. 1). See also Saldanha et al. 2020 and Saldanha (2022).

```{r ltd-hist, echo=FALSE, out.height="70%", out.width="70%", fig.align = 'center'}
library("stats")
bimodDistFunc <- function (sz,modsplt, cpar1, cpar2, vpar1, vpar2) {
  y0 <- rnorm(sz,cpar1,vpar1)
  y1 <- rnorm(sz,cpar2,vpar2)
  pct <- rbinom(sz,size=1,prob=modsplt)
  y <- y0*pct + y1*(1-pct) 
}

ExpShort<-function(x,n)
{
  short<-1:n
  for (i in 1:n)
  {
    short[i]<-sum(x[i:n]-x[i])/n
  }
  return(short)
}

bimod<-bimodDistFunc(10^6,0.8,50.2,299.3,8.4,8.4)

Q<-470
P2<-0.99
TS<-Q*(1-P2)

# TRUE
  TruROP<-275.8395759 # From the Exp 15 for P2=.99 TruROP.csv file of the LTDFillRate Project
# NORMAL
  normloss<-Q/sd(bimod)*(1-P2)
  NormROP<-optimize(function(z){abs((dnorm(z)-z*(1-pnorm(z)))-normloss)},lower=0,
                    upper=6)$minimum*sd(bimod)+mean(bimod)

# GAMMA
  mu<-mean(bimod)
  sigma<-sd(bimod)
  Gshape<-mu^2/sigma^2 
  Gscale<-mu/sigma^2
  gESC<-Q*(1-P2)
  GammaROP<-optimize(function(s){abs((Gshape/Gscale*(1-pgamma(s,Gshape+1,Gscale))-s*
                                       (1-pgamma(s,Gshape,Gscale)))-gESC)},
                    lower=0,upper=qgamma(0.99,Gshape,Gscale))$minimum

# PLOT LTD
hist(bimod,freq = FALSE,xlab = "10^6 Random Draws of Right Skew Bimodal LTD",
     col = "lightblue",main = NULL)
  abline(v=c(TruROP,NormROP,GammaROP), col=c("black","red","blue"),lwd=c(3,2,2))
  title(paste("Fig. 1. True (black), normal (red) and Gamma (blue) ROP at P2=0.99"))
  
  
```

### Note

- There are separate functions that take lead time demand data (LTD) as input and independent lead time and demand data as input marked as "x" and "ld," respectively.
- A demonstration including a limited trial for the FR target with user data is available at https://jpsaldanha.shinyapps.io/inventoRy/

The inventoRy package offers the following approaches for estimating ROP or SS for the CSL or FR targets:
  
  - Bootstrap
  - Normal
  - Gamma
  
In addition, lognormal, truncated normal and Uniform estimation approaches are provided for the FR targets as featured in Saldanha (2022)

<!--The goal of inventoRy is to assist in estimate inventory parameters -- reorder point (ROP) and safety stock (ss) -- for the fill rate and service level customer service criterion under the continuous review inventory policy.
The primary purpose of this package is to provide non-paramteric bootstrap estimation functions for cases when the lead time demand (LTD) distribution takes on non-standard forms. Functions for standard forms are also provided including for uniform, lognormal, truncated-normal, etc. as an accompaniment of the Saldanha (2022) article.
-->

# Installation

You can install the latest development version of inventoRy directly from [GitHub](https://github.com/jpsaldanha/inventoRy) with: -->

```r
install.packages("devtools")
devtools::install_github("jpsaldanha/inventoRy")
```



## Examples

Following are simple examples using the bootstrap to estimate:

1. ROP and SS with LTD for a CSL target

```{r LTD ROP-CSL}
library("inventoRy")

# Generate a vector of 24 LTD data
x<-runif(24,100,200)

# For a CSL target of 90% probability of no stockouts (PNS)

# ROP
CRboot.x.csl(x,.9)

# SS
CRboot.x.csl(x,.9,roptru=FALSE)
```

2. ROP and SS with LTD for a FR target

```{r LTD ROP-FR}
library("inventoRy")

# Generate a vector of 24 LTD data
x<-runif(24,100,200)

# For a target FR of 95%. 
# Note for FR we need to specify an order quantity (Q=100) under the continuous review inventory policy.

# ROP
CRboot.x.fr(x,100,.95)

# SS
CRboot.x.fr(x,100,.95,roptru=FALSE)
```

3. ROP and SS with independent lead time and demand for a CSL target

```{r L & D ROP-CSL}
library("inventoRy")

# Generate a vector of 20 lead-time  data
x<-runif(20,2,8)
# Generate a vector of 12 demand  data
y<-runif(12,20,40)

# For a CSL target of PNS = 90%

# ROP
CRboot.ld.csl(x,y,.9)

# SS
CRboot.ld.csl(x,y,.9,roptru=FALSE)
```

4. ROP and SS with independent lead time and demand for a FR target

```{r L & D ROP-FR}
library("inventoRy")

# Generate a vector of 20 lead-time  data
x<-runif(20,2,8)
# Generate a vector of 12 demand  data
y<-runif(12,20,40)

# For a target FR of 95%. 

# ROP
CRboot.ld.fr(x,y,100,.95)

# SS
CRboot.ld.fr(x,y,100,.95,roptru=FALSE)
```

## References

* Saldanha, J.P., 2022. Estimating the reorder point for a fill-rate target under a continuous review policy in the presence of non-standard lead-time demand distributions. Transportation Research Part E: Logistics and Transportation Review, doi.org/10.1016/j.tre.2022.102766.
* Saldanha, J.P., Price, B., Thomas, D.J., 2020. A non–parametric approach for setting safety stock levels. SSRN [online]. Available at: http://dx.doi.org/10.2139/ssrn.3624998.
* Silver, E.A., Pyke, D.F., Thomas, D.J., 2016. Inventory and Production Management in Supply Chains. 4th ed. CRC Press, Boca Raton, FL.
* Tyworth, J.E., Guo, Y., Ganeshan, R., 1996. Inventory control under gamma demand and random lead time. J. Bus. Logist. 17(1), 291–304.

